A Survey of Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
minor changes in risk/ben section.

\subsubsection{Regression Model} 
Introduce the model and what was considered in the model. Serge can probably do this better. Talk about which factors mattered, and how much, and also interesting statistics we found, if any. Also, correlations with demographics here as well!

\subsection{Risk and Benefit Rankings} 
When assessing new technologies, participants generally had rated the technologies similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today. A list of the ranking of most risky and most beneficial technologies can be see in appendix \ref{sec:techrank}; the most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).

{\color{red} can you redo the graph for figure ~\ref{fig:techplot}? I trust your judgement on how it should look and what to emphasize.}

>>>>

\subsubsection{Regression Model} 
{\color{red} SERGE TODO: fill in this section.}

\subsection{Risk and Benefit Rankings} 
When assessing new technologies, participants generally rated all new technologies and new wearables similarly, considering them low risk and low benefit (see figure \ref{fig:techplot}). We suspect that these similar assessments are because most are not consciously aware of the possibilities of these technologies or how they are being used today. A list of the ranking of most risky and most beneficial technologies can be see in appendix \ref{sec:techrank}; the most risky and most beneficial technologies reveals the list of most familiar technologies for the average user (internet, laptops, email, smartphones, etc.).

{\color{red} SERGE TODO: redo the graph for figure ~\ref{fig:techplot}.}
